\LARGE \bf Approximately Orchestrated Road Traffic Automata\\ a General Traffic Simulation Framework

### 2012-03-14 papers/itsc_2012/final.tex
Edits to abstract and intro

\begin{abstract} 
Autonomous vehicles have seen great advancements in recent years, and
such vehicles are now ever closer to being commercially available.
The advent of driver-less cars provides opportunities for optimizing
traffic in ways not possible before. This paper introduces an open
source multi-agent traffic simulator called AORTA, which stands for
\textit{Approximately Orchestrated Road Traffic Automata}, and
demonstrates its usage for optimizing autonomous traffic at a
city-wide scale. AORTA creates scale simulations by generating maps
using publicly available road data from \textit{OpenStreetMap}
(OSM). Simulations of specific regions throughout the world can be set
up in the few minutes it takes to export data for the region of
interest from OSM. AORTA focuses on interactions between agents by
defining \textit{behaviors} for individual vehicles and
intersections. These behaviors allow agents to interact with each
other as well as local intersections in any manner required for a
simulation of interest.  This is demonstrated in a simple experiment
for autonomous vehicles demonstrated at the end of this paper.
\end{abstract}

@@

The arrival of driver-less cars presents several challenges that need to be
addressed in the near term. Road infrastructure changes could provide important
improvements to traffic involving autonomous vehicles. A number of legal and
safety concerns need to be addressed in the context of driver-less cars. Human
drivers need new methodologies to interact with autonomous drivers on public roads.
AORTA aims to solve some of these problems by providing a sandbox in which such
methodologies can be found and tested for safety and efficiency before being
deployed in the real world.  In this manner, AORTA aids in the effort to find
intermediate stages between entirely human and entirely autonomous traffic.

@@

This paper introduces an open source multi-agent microscopic traffic
simulator called AORTA, which stands for \textit{Approximately
Orchestrated Road Traffic Automata}. The AORTA simulator focuses on
the interactions between individual vehicles and intersections, both
of which act as \textit{agents} in AORTA's framework. Vehicles
interact with other vehicles to pass and change lanes, and interact
with intersections to decide when to cross them. Researchers
developing applications on top of the AORTA simulator define
\textit{behaviors} that these agents follow to interact with one
another. To optimize traffic flow, external \textit{overseers} can
coordinate with these agents to provide recommendations such as route
suggestions or intersection signaling policies.  An advantage of such
an approach is that by assigning human-like behaviors such as the
``car following model'' \cite{brackstone1999car} to vehicles, and
traffic-signal-like policies to intersection, AORTA can just as easily
simulate human traffic.

@@

\commentpk{Needs 1 more para based on final application}

% Section 2 will review other traffic simulators. Section 3 will introduce the
% overall architecture of AORTA. Section 4 describes how OSM maps are used.
% Section 5 explains the simulation engine and the properties AORTA posses that
% are useful for general traffic experiments. Section 6 gives some initial
% results from such an experiment, and Section 7 concludes.

>>>>

\begin{abstract} 
Autonomous vehicles have seen great advancements in recent years, and
such vehicles are now ever closer to being commercially available.
The advent of driver-less cars provides opportunities for optimizing
traffic in ways not possible before. This paper introduces an open
source multi-agent traffic simulator called AORTA, which stands for
\textit{Approximately Orchestrated Road Traffic Automata}, and
demonstrates its usage for optimizing autonomous traffic at a
city-wide scale. AORTA creates scale simulations by generating maps
using publicly available road data from \textit{OpenStreetMap}
(OSM). Simulations of specific regions throughout the world can be set
up in the few minutes it takes to export data for the region of
interest from OSM. AORTA focuses on interactions between agents by
defining \textit{behaviors} for individual vehicles and
intersections. These behaviors allow agents to interact with each
other as well as local intersections in any manner required for a
simulation of interest.  This is demonstrated in a simple experiment
for autonomous vehicles presented at the end of this paper.
\end{abstract}

@@

The arrival of driver-less cars presents several challenges that need to be
addressed in the near term. Road infrastructure changes could provide important
improvements to traffic involving autonomous vehicles. A number of legal and
safety concerns need to be addressed in the context of driver-less cars. Human
drivers need new methodologies to interact with autonomous drivers on public roads.
This work aims to solve some of these problems by providing a sandbox in which such
methodologies can be found and tested for safety and efficiency before being
deployed in the real world.  In this manner, the present work aids in the effort to find
intermediate stages between entirely human and entirely autonomous traffic.

@@

This paper introduces an open source multi-agent microscopic traffic
simulator called AORTA, which stands for \textit{Approximately
Orchestrated Road Traffic Automata}. The AORTA simulator focuses on
the interactions between individual vehicles and intersections, both
of which act as \textit{agents} in AORTA's framework. Vehicles
interact with other vehicles to pass and change lanes, and interact
with intersections to decide when to cross them. Researchers
developing applications on top of the AORTA simulator define
\textit{behaviors} that these agents follow to interact with one
another. An advantage of such an approach is that by assigning
human-like behaviors such as the ``car following model''
\cite{brackstone1999car} to vehicles, and traffic-signal-like
policies to intersections, AORTA can just as easily simulate human
traffic.

@@

After exploring the state of the art \ref{sec:related_work} and explaining
the architecture of AORTA \ref{sec:arch} as well as its use of OSM \ref{sec:map},
we will describe simulation in AORTA \ref{sec:simulation} and how to extend it
\ref{sec:config}, concluding with an example experiment \ref{sec:results}.
In this final experiment, AORTA shows the benefits of an AIM-inspired
\cite{JAIR08-dresner} reservation intersection policy over traditional
traffic signals and stop signs.
